Network based multifactorial modelling microRNA-target interaction.

### 2019-08-22 article.Rmd
article todo

[#TODO]: <> "about formulas, 1) eq:3 F/Fmax can be removed, 2) in formulas eq:1 and eq:2, C_m or Eff_gi is not intuitive, is there consensus terms about effect or nth gene?"

>>>>

[#TODO]: <> "about formulas, 2) in formulas eq:1 and eq:2, C_m or Eff_gi is not intuitive, is there consensus terms about effect or nth gene?"
